White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2016-01-27 papers/wdmerger_II/paper.tex
rho -> \rho

In a hydrostatic burn, we keep $\rho$ and $T$ fixed throughout, and use
the energy released at the end to compute a final temperature that is
thermodynamically consistent with the new internal energy. By contrast,
in a self-heating burn, we allow the temperature to evolve in response
to the burning (see \citet{maestro3}):
\begin{equation}
  \frac{dT}{dt} = \frac{1}{c_V}\left(\frac{\partial e}{\partial t} - \sum_n \frac{\partial e}{\partial X_n}\frac{\partial X_n}{\partial t}\right)
\end{equation}
Here $c_V$ is the specific heat at constant volume, and $(\partial e/\partial X_n)$
is the derivative of the internal energy with respect to the mass fraction of a given
species (with other thermodynamic variables held constant). Both quantities are provided by the
equation of state. During this burn, we can keep these thermodynamic
derivatives constant using their value at the beginning of the run, or at each step we
can choose to re-evaluate the equation of state using the latest value of $(rho, T)$.
The latter is more expensive but also more accurate, and we use it in this paper.
A third option presented by \citet{raskin:2010} is a so-called ``hybrid'' mode.
In this mode, by default we do a hydrostatic burn. If that burn fails, or if the net
energy change is negative, we do the burn again in self-heating mode. All three options
are implemented in our burner software.

>>>>

In a hydrostatic burn, we keep $\rho$ and $T$ fixed throughout, and use
the energy released at the end to compute a final temperature that is
thermodynamically consistent with the new internal energy. By contrast,
in a self-heating burn, we allow the temperature to evolve in response
to the burning (see \citet{maestro3}):
\begin{equation}
  \frac{dT}{dt} = \frac{1}{c_V}\left(\frac{\partial e}{\partial t} - \sum_n \frac{\partial e}{\partial X_n}\frac{\partial X_n}{\partial t}\right)
\end{equation}
Here $c_V$ is the specific heat at constant volume, and $(\partial e/\partial X_n)$
is the derivative of the internal energy with respect to the mass fraction of a given
species (with other thermodynamic variables held constant). Both quantities are provided by the
equation of state. During this burn, we can keep these thermodynamic
derivatives constant using their value at the beginning of the run, or at each step we
can choose to re-evaluate the equation of state using the latest value of $(\rho, T)$.
The latter is more expensive but also more accurate, and we use it in this paper.
A third option presented by \citet{raskin:2010} is a so-called ``hybrid'' mode.
In this mode, by default we do a hydrostatic burn. If that burn fails, or if the net
energy change is negative, we do the burn again in self-heating mode. All three options
are implemented in our burner software.
